Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-05-30 ms.tex
incorporated the corrections and suggestions from Kento.

\author{Kento Masuda?}
\affiliation{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}

@@

\begin{abstract}
KIC 12557548 b is one of several disintegrating planet candidates which lose mass in the form of dust particles escaping their surface.
Photometric monitoring of KIC 12557548 b originally showed evidence for a slowdown of integration activity in 2013 and 2014.
Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
We also evaluate high resolution archival spectra from the Subaru HDS spectrograph and find spectra consistent with a main-sequence T=4500 $\pm$110 K star.
\end{abstract}

@@

The underlying planet candidate \sha\ has not been detected directly, but several observational constraints have placed upper limits on its size and mass.
High precision radial velocity measurements of the host star with Keck/HIRES put an upper limit on the reflex motion due to the planet and constrains the mass to be $\lesssim 1.2 M_{\mathrm Jup}$ \citep{croll2014}.
\citet{masuda2018rvKIC1255} find that the upper limit on the radial velocity semi-amplitude is 86 km/s corresponding to a planet mass $\lesssim 0.28 M_{\mathrm Jup}$ using the Subaru High Dispersion Spectrometer (HDS).
There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km \citep{vanWerkhoven2014}.
A radiative-hydrodynamic wind model predicts that the mass loss rate will be a strong function of planet mass and for the present-day mass loss rate of $\sim$ M$_\oplus/Gyr$, the modeled mass is 0.014 $M_\oplus$.

@@

\begin{figure}[!hbtp]
\begin{centering}
\includegraphics[width=0.7\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
\caption{Median spectrum of \shStar\ (reduced by Kento Masuda) near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZ}
\end{centering}
\end{figure}

@@

\section{Acknowledgements}
%Thanks to Alessondra Springman for good resources on core and mantle compositions and the gases that could sublimate off of them.
%Thanks to Jonathan Fraine and Rafia Bushra for help with observing at the 61-inch Kuiper telescope on Mt Bigelow.
%MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.
This research made use of the \texttt{astropy} package \citep{astropy2013}.

>>>>

%\author{Kento Masuda?}
%\affiliation{Department of Astrophysical Sciences, Princeton University, Princeton, NJ 08544, USA}

@@

\begin{abstract}
KIC 12557548 b is one of several disintegrating planet candidates which lose mass in the form of dust particles escaping their surface.
Photometric monitoring of KIC 12557548 b originally showed evidence for a slowdown of disintegration activity in 2013 and 2014.
Here, we report 2016 measurements that are consistent with photometry from the Kepler spacecraft in 2009-2013.
We also evaluate high resolution archival spectra from the Subaru HDS spectrograph and find spectra consistent with a main-sequence T=4500 $\pm$110 K star.
\end{abstract}

@@

The underlying planet candidate \sha\ has not been detected directly, but several observational constraints have placed upper limits on its size and mass.
High precision radial velocity measurements of the host star with Keck/HIRES put an upper limit on the reflex motion due to the planet and constrains the mass to be $\lesssim 1.2 M_{\mathrm Jup}$ \citep{croll2014}.
\citet{masuda2018rvKIC1255} find that the upper limit on the radial velocity semi-amplitude is 86 m/s corresponding to a planet mass $\lesssim 0.28 M_{\mathrm Jup}$ using the Subaru High Dispersion Spectrometer (HDS).
There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km \citep{vanWerkhoven2014}.
A radiative-hydrodynamic wind model predicts that the mass loss rate will be a strong function of planet mass and for the present-day mass loss rate of $\sim$ M$_\oplus/Gyr$, the modeled mass is 0.014 $M_\oplus$.

@@

\begin{figure}[!hbtp]
\begin{centering}
\includegraphics[width=0.7\textwidth]{images/subaru/bosz_mg_triplet_median_spec_w_5000.pdf}
\caption{Median spectrum of \shStar\ \citep{} near the Mg triplet compared to 4500 K BOSZ models with two different log(g)s.}\label{fig:mgTripletBOSZ}
\end{centering}
\end{figure}

@@

\section{Acknowledgements}
%Thanks to Alessondra Springman for good resources on core and mantle compositions and the gases that could sublimate off of them.
%Thanks to Jonathan Fraine and Rafia Bushra for help with observing at the 61-inch Kuiper telescope on Mt Bigelow.
%MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
Thanks to Kento Masuda for sharing the 2015 Subaru spectrum of \shStar\ and giving helpful comments on this work.
Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.
